### 2022-08-08 draft.tex
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@2c9b6ff5150b9f0aa82a66d3a5535a4721e5b462 🚀

@@

@@

We tested our analytical and heuristic MaxEnt models against open
food-web data queried from three different sources and integrated into
what we call our \emph{complete dataset}. These sources include (1)
terrestrial and aquatic food webs sampled globally and archived on the
ecological interactions database Mangal; (2) freshwater stream food webs
from New Zealand; and (3) aquatic food webs from Tuesday Lake (Michigan,
United States). First, all food webs archived on \texttt{mangal.io}
(Poisot et al. 2016; Banville, Vissault, and Poisot 2021) were directly
queried from the database (\(n = 235\)). Most ecological networks
archived on Mangal are multilayer networks, i.e.~networks that describe
different types of interactions. We kept all networks whose interactions
were mainly of predation and herbivory types, and removed the largest
network (\(S = 714\)) for computational efficiency reasons. Then, to
this set we added food webs from two different sources: the New-Zealand
dataset (\(n = 21\); Pomeranz et al. 2018) and the Tuesday lake dataset
(\(n = 2\); Cohen, Jonsson, and Carpenter 2003). Of these two datasets,
\(19\) networks had data on species' relative abundances that were used
in the neutral model (Box 2). These \(19\) networks constitute our
\emph{abundance dataset}, which is a subset of our complete dataset.

@@

@@

@@

@@

>>>>

\hypertarget{the-constrained-structure-of-ecological-networks}{%
\subsection{The constrained structure of ecological
networks}\label{the-constrained-structure-of-ecological-networks}}

A variety of measures of the structure of ecological networks have been
used to describe the organization of species interactions in a
biological community (Delmas et al. 2019). These measures provide
valuable information on the functioning of ecosystems and their
responses to environmental change (e.g., Pascual and Dunne 2006; Gómez,
Perfectti, and Jordano 2011). For instance, Bascompte et al. (2003)
suggest that plant--pollinator and seed-disperser networks have a highly
nested structure that can promote species persistence. Another example,
in food webs, shows that a high connectance can promote the robustness
of the system to species lost (Dunne, Williams, and Martinez 2002).
However, despite the growing literature on the ecological implications
of network structure, the association between many of these measures
impedes our ability to fully understand what drives the structure and
behavior of ecological networks. In particular, nestedness and
modularity are strongly associated in ecological networks (Fortuna et
al. 2010), and network connectance has been shown to be an important
driver of many other emerging network properties (Timothée Poisot and
Gravel 2014). In light of these observations, it is difficult to assess
whether attributed effects of given properties are the artifacts of
other, perhaps simpler, measures. It might be necessary to factor out
the effect of other correlated measures before analyzing the structure
of ecological networks.

One way to tackle this issue is first to recognize that food webs and
other ecological networks are constrained systems. In other words, the
space of possible network configurations shrinks as we know more about a
network structure. Consequently, the range of values that a given
network property can take depends on the values of other properties.
Above all, the structure of ecological networks is constrained by the
number of species, or nodes, present. Food webs with high species
richness typically have a lower connectance (MacDonald, Banville, and
Poisot 2020) than smaller networks. This is because the number of
realized interactions in empirical food webs scales slower than the
number of possible species pairs (MacDonald, Banville, and Poisot 2020).
As shown by Timothée Poisot and Gravel (2014), connectance itself can
constrain different aspects of network structure such as the degree
distribution. Other measures, such as the maximum trophic level, can
also constrain the space of feasible networks.

@@

\hypertarget{objectives}{%
\subsection{Objectives}\label{objectives}}

@@

We tested our analytical and heuristic MaxEnt models against open
food-web data queried from three different sources and integrated into
what we call our \emph{complete dataset}. These sources include (1)
terrestrial and aquatic food webs sampled globally and archived on the
ecological interactions database Mangal; (2) freshwater stream food webs
from New Zealand; and (3) aquatic food webs from Tuesday Lake (Michigan,
United States). First, all food webs archived on \texttt{mangal.io}
(Timothee Poisot et al. 2016; Banville, Vissault, and Poisot 2021) were
directly queried from the database (\(n = 235\)). Most ecological
networks archived on Mangal are multilayer networks, i.e.~networks that
describe different types of interactions. We kept all networks whose
interactions were mainly of predation and herbivory types, and removed
the largest network (\(S = 714\)) for computational efficiency reasons.
Then, to this set we added food webs from two different sources: the
New-Zealand dataset (\(n = 21\); Pomeranz et al. 2018) and the Tuesday
lake dataset (\(n = 2\); Cohen, Jonsson, and Carpenter 2003). Of these
two datasets, \(19\) networks had data on species' relative abundances
that were used in the neutral model (Box 2). These \(19\) networks
constitute our \emph{abundance dataset}, which is a subset of our
complete dataset.

@@

\leavevmode\hypertarget{ref-Dunne2002NetStrb}{}%
Dunne, Jennifer A., Richard J. Williams, and Neo D. Martinez. 2002.
{``Network Structure and Biodiversity Loss in Food Webs: Robustness
Increases with Connectance.''} \emph{Ecology Letters} 5 (4): 558--67.
\url{https://doi.org/10.1046/j.1461-0248.2002.00354.x}.

@@

\leavevmode\hypertarget{ref-Gomez2011FunConb}{}%
Gómez, José M., Francisco Perfectti, and Pedro Jordano. 2011. {``The
Functional Consequences of Mutualistic Network Architecture.''}
\emph{PLOS ONE} 6 (1): e16143.
\url{https://doi.org/10.1371/journal.pone.0016143}.

@@

\leavevmode\hypertarget{ref-Pascual2006EcoNeta}{}%
Pascual, Department of Ecology and Evolutionary Biology Mercedes, and
Visiting Professor Jennifer A. Dunne. 2006. \emph{Ecological Networks:
Linking Structure to Dynamics in Food Webs}. Oxford University Press,
USA.

@@

\leavevmode\hypertarget{ref-Poisot2014WheEcoa}{}%
Poisot, Timothée, and Dominique Gravel. 2014. {``When Is an Ecological
Network Complex? Connectance Drives Degree Distribution and Emerging
Network Properties.''} \emph{PeerJ} 2: e251.
\url{https://doi.org/10.7717/peerj.251}.
